---
title: "dplyr Cheatsheet"
output: 
  blogdown::html_page
date: "2020-05-01"
author: Ling
GHissueID: 1
categories:
  - notes
  
tags: 
  - R
  - dplyr
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



See `dplyr` cheatsheet [here](https://rstudio.com/wp-content/uploads/2015/02/data-wrangling-cheatsheet.pdf). Remark: There is conflict between the `dplyr` package and `MASS` package, the `select` function, in particular, can cause problem. Remember to check your environment before implement the program! Another solution is to add `dplyr::` before the functions from `dplyr` package. This can be helpful especially when you are coding in a big team where people use different packages and environments.



```{r }
library(dplyr)
data("iris")
species <- unique(iris$Species)
## Manually created ID mapping
map <- data.frame(ID = 1:length(species), Species = species); map
## Manually created Missing data
iris[1:3,2] = NA
## A peak of current dataset
head(iris)
```


```{r}
##### ROWS
df = iris %>% 
  mutate_all(~replace (., is.na(.), 0)) %>% ## Replace NA with 0 
  filter(!is.na(Sepal.Width)) %>% ## Select rows without NA in Sepcal.Width
  mutate(Sepal.Length= replace(Sepal.Length, Sepal.Length>5, "large") ) %>%## Replace entries with condition
  mutate(Sepal.Length= replace(Sepal.Length, Sepal.Length<=5, "small") )  %>% 
  mutate(Species = gsub(' ','', Species)) %>% ## 
  mutate(Species = tolower(Species)) ## toupper: uppercase, tolower: lowercase
head(df)

#### COLUMNS
df2 = iris%>%
  right_join(map, by = "Species") %>% ## Join according to the right matrix
  select(Sepal.Length, Petal.Width, ID) %>% ## Select columns
  select( - c(Petal.Width) ) ## Delete columns
head(df2)
```